Bayesian Exploration in Deep Reinforcement Learning

### 2022-02-03 papers/main.tex
TEMPORARY DEPLOY COMMIT

\subsection{Noisy Networks}
NoisyNet, specifically, is a stochastic
process represented by a neural network with stochastic weights. We will define
this parameterized function as \(g_\phi\), and their sampling distribution as
\(\rho_\phi \in \mathcal{P}\). Given a noise vector \(\xi\), we have
\(f(\bm{s}, \bm{a}) = g_\phi(\bm{a}, \bm{s}, \xi)\). Although this means
that NoisyNet can model stochastic policies, \citet{fortunato_noisy_2019} point
out that for the loss function it is optimising, there always exsists a deterministic
optimal policy. They show through emipirical analysis, however, that this does not
mean that the policy necessarily disregards the noise and converges to a deterministic
policy.

@@

\begin{multline}\label{eq:fkl}
    \nabla_\phi \KL[q_\phi(\f(\X)) \Vert p(\f(\X))] = \E_\rho)\phi \left[ \nabla_\phi \log \rho_\phi (\f(\X)) \right]\\
    + \E_\xi \left[ \nabla_\phi \f(\X)( \nabla_\f \log \rho_\phi(\f(\X)) - \nabla_\f \log p(\f(\X))) \right].
\end{multline}

>>>>

\subsection{Noisy Networks}
NoisyNet can be viewed as a stochastic
process represented by a neural network with stochastic weights. We will define
this parameterized function as \(g_\phi\), and their sampling distribution as
\(\rho_\phi\). Given a noise vector \(\xi\), we have
\(f(\bm{s}, \bm{a}) = g_\phi(\bm{a}, \bm{s}, \xi)\). Although this means
that NoisyNet can model stochastic policies, \citet{fortunato_noisy_2019} point
out that for the mean squared error loss in DQN, there always exsists a deterministic
optimal policy. They show through emipirical analysis, however, that this does not
mean that the policy necessarily disregards the noise and converges to a deterministic
policy.

@@

\begin{multline}\label{eq:fkl}
    \nabla_\phi \KL[q_\phi(\f(\X)) \Vert p(\f(\X))] = \E_{\rho_\phi} \left[ \nabla_\phi \log \rho_\phi (\f(\X)) \right]\\
    + \E_\xi \left[ \nabla_\phi \f(\X)( \nabla_\f \log \rho_\phi(\f(\X)) - \nabla_\f \log p(\f(\X))) \right].
\end{multline}
